### 2015-05-12 whoop.tex
updates to SMACK text

\ADComment{Explain how pointers get handled (SMACK) -- be brief, talk about memory regions, don't show Boogie code.}

\medskip\noindent\textbf{Translation to Boogie IVL }
%
Next, the rewritten program is passed to Clang which compiles it to LLVM-IR~\cite{lattner2004llvm}, a low-level assembly-like language in single static assignment (SSA) form. SMACK then translates the LLVM-IR to Boogie IVL. SMACK leverages the pointer-alias analyses of LLVM to efficiently model the heap manipulation operations of the original program in Boogie IVL. To achieve scalability, SMACK is using a split-memory model instead of a monolithic one that would be difficult for backend verifiers to reason about~\cite{rakamaric2009scalable}.

The function \texttt{\$pa} models pointer arithmetic, while the map \texttt{\$M.0} is a memory region that typically denotes a shared resource. Notice that function calls (e.g. to lock and unlock a mutex) are preserved in the translation.

>>>>

\medskip\noindent\textbf{Translation for Verification }
%
The rewritten, by Chauffeur, driver is compiled by Clang to LLVM-IR~\cite{lattner2004llvm}, a low-level assembly-like language in single static assignment (SSA) form. SMACK then translates the LLVM-IR to Boogie IVL. Function calls (e.g. to lock and unlock a mutex) are preserved in this translation, which is useful for the lockset instrumentation performed by \whoop.

SMACK leverages the pointer-alias analyses of LLVM to efficiently model the heap manipulation operations of C programs in Boogie IVL. To achieve scalability, SMACK is using a split-memory model instead of a monolithic one that would be difficult for backend verifiers to reason about~\cite{rakamaric2009scalable}. This split memory model is based on \emph{memory regions}, which are maps of integers that model the heap.

A benefit of using this SMACK model is that memory regions denote disjoint sections of the heap (i.e. pointers that cannot alias). We leverage this knowledge inside \whoop to guide and optimize our instrumentation and analysis. In reality, this memory model is unsound ... (e.g. integers, overflow?), but for our work we assume it is sound.
